---
title: "a7 Collaboration"
subtitle: "World Data Visualization Dataset"
authors: "Bernabe Ibarra | Feng Yu Yeh | Sean Le | Thomas That"
date: "2019-02-25"
output:
  html_document:
      smooth_scroll: TRUE
---

<style>
body{
  font-family: 'Verdana', Georgia;
  font-size: 15px;
}

h1,h3,h4 {
  font-family: 'Helvetica', Georgia;
}

h1{
  background-color: #2364AA;
  color: #3DA5D9;
  text-shadow: 2px 2px 4px #000000;
  font-family: 'Impact', Georgia;
  padding: 20px;
}

.container { width: 1000px; }

h2{
  background-color: #73BFB8;
  color: #ffffff;
  font-weight: bolder;
  font-family: 'Verdana', Georgia;
  text-shadow: 1px 1px 2px #000000;
}

h3{
  color: #2364AA;
  font-family: 'Verdana', Georgia;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
source("scripts/list_info.R")
source("scripts/summary_calculations.R")
source("scripts/Graph1.R")
source("scripts/chart2.R")
library(knitr)
library(dplyr)
library(plotly)
library(ggplot2)
wdvp_df <- read.csv("data/wdvp.csv", stringsAsFactors = F)
```

## Summary

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
answers <- summary_calculations(wdvp_df)
avg_1 <- round(answers$avg_health_expenditure_pct, 1)
avg_2 <- round(answers$avg_world_happiness, 1)
avg_3 <- round(answers$avg_health_expenditure_per_person, 1)
```
The World Data Visualization dataset describes countries using over 30 attributes. Our group came up with cross-national averages of health expenditure, world happiness, and expenditure per person. The averages are as follows:

#### Mean Average Between Countries
- Health Expenditure PTC = **`r avg_1`**
- World Happiness = **`r avg_2`**
- Health Expenditure Per Person = **`r avg_3`**


## Visualization 1:
This graphs the average happiness score using ggplot.

```{r message=FALSE, warning=FALSE}
viz_1 <- make_graph(wdvp_df)
viz_1
```

## Visualization 2:

This graphs the the unemplyment rate using Plotly.

# ```{r}
# viz_2 <- chart_2(wdvp_df)
# viz_2
# ```

