---
title: "a7 Collaboration"
subtitle: "Blank Dataset"
authors: "Bernabe Ibarra | Feng Yu Yeh | Sean Le | Thomas That"
date: "2019-02-25"
output:
  html_document:
      smooth_scroll: TRUE
---

<style>
body{
  font-family: 'Verdana', Georgia;
  font-size: 15px;
}

h1,h3,h4 {
  font-family: 'Helvetica', Georgia;
}

h1{
  background-color: blue;
  color: #FFFFFF;
  text-shadow: 2px 2px 4px #000000;
  font-family: 'Impact', Georgia;
  padding: 20px;
}

.container { width: 1000px; }

h2{
  background-color: green;
  color: #FFFFFF;
  font-family: 'Heletica', Georgia;
  text-shadow: 1px 1px 2px #000000;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
source("scripts/list_info.R")
source("scripts/chart2.R")
source("scripts/Graph1.R")
source("scripts/summary_calculations.R")
library(knitr)
library(dplyr)
library(plotly)
library(ggplot2)
wdvp_df <- read.csv("data/wdvp.csv", stringsAsFactors = F)

```

## Summary
mean average
avg_health_expenditure_pct
avg_world_happiness
avg_health_expenditure_per_person

```{r}
answers <- summary_calculations(wdvp_df)
answers$avg_health_expenditure_pct
answers$avg_world_happiness
answers$avg_health_expenditure_per_person
```

**(citing at least 3 values calculated from the data)**


## Visualization 1:
This graphs the average happiness score using ggplot.

```{r}
viz_1 <- make_graph(wdvp_df)
viz_1
```

## Visualization 2:

This graphs the the unemplyment rate using Plotly.



